Walkability

### 2020-11-04 EPA:Census Team/Gretchen Walkability/Walkability Data Manip.Rmd
Updated Walkability Plots

```{r}
library(leaflet)
library(rgdal)
library(tidyverse)
library(dplyr)
library(RColorBrewer)
library(stringr)
library(ggplot2)

#get data
walk <- readOGR(dsn = "Natl_WI_SHP/Natl_WI.shp")
mwalk <- walk[walk$SFIPS == "26", ]

statefips <- read.csv("~/Documents/Columbia/Practicum - Aracelis Torres/Data/Walkability/State FIPS.csv")
```

```{r}
# Walkability map (Michigan Specific) 
## Target End state: blue water, data for whole country, better names, search by zip code/location, round Walkability Index Score, add layers for parks/schools/nature???
walkmap <- leaflet(mwalk) %>%
 setView(lat = 44.2444, lng = -86.3243, zoom = 6) %>%
 addProviderTiles(providers$Stamen.TonerLite) %>%
  #add bloc borders
 addPolygons(stroke = TRUE, smoothFactor = 0.5,
  weight=1, color='#333333', opacity=1, 
  #chloropleth shading
  fillColor = ~colorQuantile("Greens", NatWalkInd)(NatWalkInd), 
  fillOpacity = 1, 
  #add pinpoint label
  label = ~stringr::str_c(CBSA_Name, ' ',
          formatC(NatWalkInd, big.mark = ',', format='f')),
  labelOptions = labelOptions(direction = 'auto'),
  #add hover highlight
  highlightOptions = highlightOptions(
          color='#000000', weight = 3,
          bringToFront = TRUE, sendToBack = TRUE))

@@

>>>>

```{r}
library(leaflet)
library(rgdal)
library(tidyverse)
library(dplyr)
library(RColorBrewer)
library(stringr)
library(ggplot2)
library(plotly)

#get data
walk <- readOGR(dsn = "Natl_WI_SHP/Natl_WI.shp")
mwalk <- walk[walk$SFIPS == "26", ]
#writeOGR(mwalk, ".", "mwalk", driver="ESRI Shapefile")
mwalk2 <- readOGR(dsn = "mwalk.shp")

statefips <- read.csv("~/Documents/Columbia/Practicum - Aracelis Torres/Data/Walkability/State FIPS.csv")
countyfips <- read.csv("FIPS and County Names.csv")
```

```{r}
# Walkability map (Michigan Specific) 
## Target End state: blue water, better names, search by zip code/location, round Walkability Index Score, add points/layers for parks/schools/nature
walkmap <- leaflet(mwalk) %>%
 setView(lat = 44.2444, lng = -86.3243, zoom = 6) %>%
 addProviderTiles(providers$Stamen.TonerLite) %>%
  #add bloc borders
 addPolygons(stroke = TRUE, smoothFactor = 0.5,
  weight=1, color='#333333', opacity=1, 
  #chloropleth shading
  fillColor = ~colorQuantile("Greens", NatWalkInd)(NatWalkInd), 
  fillOpacity = 1, 
  #add pinpoint label
  label = ~stringr::str_c(CBSA_Name, ' ',
          formatC(NatWalkInd, big.mark = ',', format='f')),
  labelOptions = labelOptions(direction = 'auto'),
  #add hover highlight
  highlightOptions = highlightOptions(
          color='#000000', weight = 3,
          bringToFront = TRUE, sendToBack = TRUE))

@@

# plot Walkability by County
# just Michigan 
walkmi <- walkwithstates %>% filter(`State Code` == 26)
walkmi$countyfips <- paste(walkmi$`State Code`, walkmi$CFIPS, sep = "")
countyfips$X1001 <- as.character(countyfips$X1001)
walkmi <- left_join(walkmi, countyfips, by = c("countyfips" = "X1001"))
walkmi <- walkmi %>% group_by(Autauga) %>% 
              summarize("Walkability" = mean(`NatWalkInd`))
colnames(walkmi) <- c("County", "Walkability")
#write_csv(walkmi, "walkmi.csv")

#Plot it 
#Reorder Walkability in table to make chart pretty
walkmi <- transform(walkmi, `County` = reorder(`County`, -Walkability))
#plot it 
 plotc <- ggplot(walkmi, aes(x=County, y=Walkability)) + 
  geom_bar(stat="identity", width=.8, fill="tomato3") + 
  coord_flip() +
  labs(title="Walkability by County",
       caption="source: EPA") + 
  theme(axis.text.y=element_text(size= 5))
ggplotly(plotc)
